\chapter{Running the demonstration application}

This section explains how to run the demonstration application and how to interact with it.  

\section{Running the programs}
The demo program is written in python 2.7.2. It requires pygame 1.9.1, simplejson 2.1.6, docopt 0.6.1 and gevent 0.13.0. 

It is delivered with a Bash-script named testrun\_2clients.sh that starts the server and two clients. 

The server and clients can also be started separately, but the server must be started first since the clients have no autodiscovery. The server requires no parameters and can be started as shown below. 

\begin{verbatim}
$ python server.py
there is no soundcard
\end{verbatim}

Starting the clients requires some flags to be specified. The --help flag displays the flags the client takes as arguments on startup. 

\begin{verbatim}
$ python client.py --help
Client rendering graphics

Usage:
  client.py [--port=<nr>]
            [--framerate=<frame/s>]
            [--x=<pixels>]
            [--y=<pixels>]
            [--pos <x1> <y1> <x2> <y2>]
  client.py (-h | --help)
  client.py --version

Options:
  -h --help     Show this screen.
  --version     Show version.
  --port=<nr>   Port number to bind to client [default: 5007].
  --framerate=<frame/s> Client framerate [default: 0].
  --x=<pixels> Width of client screen [default: 300].
  --y=<pixels> Height of client screen [default: 300].
  --pos <x1> <y1> <x2> <y2> Position of the part of the animation the client shows.
\end{verbatim}


\section{Emulating network delays}
\label{netem}
In the beginning of the development the emulated network-delays were inserted using an gevent.sleep for a variable time in the code. This variable could be specified from command line. This was replaced by using netem \footnote{\url{http://www.linuxfoundation.org/collaborate/workgroups/networking/netem}}, a more flexible solution. 

With netem, delays can be bound to specific ports. The current version therefore requires the clients to be bound to specific ports in order to test them on ports with preset delays. The port to bind the client to must be specified when starting the client, using the --port flag. 

\begin{figure}[h! ]
\begin{verbatim}[]
tc qdisc add dev lo handle 1: root htb

tc class add dev lo parent 1: classid 1:1 htb rate 1000Mbps

tc class add dev lo parent 1:1 classid 1:11 htb rate 100Mbps
tc class add dev lo parent 1:1 classid 1:12 htb rate 100Mbps
tc class add dev lo parent 1:1 classid 1:13 htb rate 100Mbps

tc qdisc add dev lo parent 1:11 handle 10: netem delay 40ms
tc qdisc add dev lo parent 1:12 handle 20: netem delay 20ms
tc qdisc add dev lo parent 1:13 handle 30: netem delay 0ms

tc filter add dev lo protocol ip prio 1 u32 match ip dport 10001 0xffff flowid 1:11
tc filter add dev lo protocol ip prio 1 u32 match ip dport 10002 0xffff flowid 1:12
tc filter add dev lo protocol ip prio 1 u32 match ip dport 10003 0xffff flowid 1:13

tc filter add dev lo protocol ip prio 1 u32 match ip sport 10001 0xffff flowid 1:11
tc filter add dev lo protocol ip prio 1 u32 match ip sport 10002 0xffff flowid 1:12
tc filter add dev lo protocol ip prio 1 u32 match ip sport 10003 0xffff flowid 1:13
\end{verbatim}
\caption{Setting delays on port 10001, 10002 and 10003}
\end{figure}

\begin{figure}[h!]
\begin{verbatim}
tc qdisc del dev lo root
\end{verbatim}
\caption{Removing delays set on dev}
\end{figure}

\section{Interacting with the server}
%FIXME
The pygame window of the server captures the events. When clicked at it will display an animation that changes the color of a cube and changes it back. By holding down the right mouse button the cube can be moved. By pressing any keyboard key a sync event is sent from the server to all clients. 

\section{Communication}
The server continously accepts new connections but if the clients lose their connection to the server they will not automatically reconnect. This means that if the server should crash, the clients lose their connection to the server and the connection will not be reestablished by restarting the server.

